\chapter{Learn About Word 2007}\label{ch:learnword}

\section{Word 2007 and Compatibility}
Because IT has installed Microsoft Office Compatibility Pack for 2007, anyone at the SEI who uses previous versions of Word can open documents that are saved in the Word 2007 format. However, Word 2003 users may not be able to change some items that were created by using Word 2007-specific new or enhanced features. For example, if you use a previous version of Word to open a document that contains equations, the equations will become images that cannot be edited.

To create a document that will be used in a previous version of Word, you should work in Compatibility Mode. Compatibility Mode ensures that no new or expanded features in Word 2007 are available while you are working in a document, so that people who are using previous versions of Word will have full editing capabilities.

\subsection{Turn on Compatibility}
When you create a new document that will be used in a previous version, in Word 2007, you can turn on Compatibility Mode by saving the file in Word 97-2003 format.
\begin{enumerate}
\item Click the Microsoft Office Button and then click Save As. 
\item Select Word 97-2003 Document in the Save as type list. 
\item In the File name box, type a name for the document. 
\item Click Save.
\end{enumerate}

\subsection{Use Feature Refresh}
\textit{Feature refresh} allows features that have been altered by compatibility mode to be made available again when a file is re-opened in Word 2007. For example, a chart that was created in Word 2007 and that is altered by compatibility mode to be an uneditable image in a previous version of Word will be fully editable again when re-opened in Word 2007.

\textbf{Important}: Not all content can be refreshed in the 2007 Office release after it has been down-graded to a previous version. For a list of features that are affected by compatibility mode, with notes on those that can be refreshed when re-opened in the 2007 Office release, see Table \ref{table2}.

\begin{center}
\begin{longtable}{p{1.1in} p{1.38in} p{3.35in}}
\caption{Word 2007 Features that are affected by Compatibility Mode}{} \label{table2} \\
Name & Note & Compatibility Mode Behavior \\
Themes & Themes are new to Word 2007. & \begin{tabular}[c]{@{}l@{}}Themes are permanently converted to styles.\\The Themes UI is disabled in compatibility mode.\end{tabular} \\
Colors (Theme Chunk) & Themes are new to Word 2007. & \begin{tabular}[c]{@{}l@{}}Themes are permanently converted to styles. \\   The Themes UI is disabled in compatibility mode.\end{tabular} \\
Font (Theme Chunk) & Themes are new to Word 2007. & \begin{tabular}[c]{@{}l@{}}Themes are permanently converted to styles. \\   The Themes UI is disabled in compatibility mode.\end{tabular} \\
Effects (Theme Chunk) & Themes are new to Word 2007. & \begin{tabular}[c]{@{}l@{}}Themes are permanently converted to styles. \\   The Themes UI is disabled in compatibility mode.\end{tabular} \\
Content Controls & Content controls are new to Word 2007. & Content controls are permanently converted to static text. The Content Controls UI is disabled in compatibility mode. \\
Tracked Moves & Tracked moves are new to Word 2007. & Tracked moves are permanently converted to ``Insert'' and ``Delete.'' \\
Relative Text Boxes & The ability to set the position of a text box relative to some part of a document. Relative text boxes are new to Word 2007. & Relative positioning of text boxes is permanently converted to absolute positioning. \\
Margin Tabs & Margin tabs are new to Word 2007. & Margin tabs are permanently converted to absolutely defined tabs. \\
Placeholder text & New to Word 2007.. & Placeholder text is permanently converted to static text. \\
Office Art 2007 & Office Art engine is improved upon in the 2007 Office release. & All Office Art 2007 objects are converted to Office 97-2003 objects. These objects are refreshed when the document is converted. When a user selects SmartArt in Word 2007, the Diagram Gallery from Word 2003 appears. \\
SmartArt Diagram & Some diagrams are new to the 2007 Office release. & Diagrams in the 2007 Office release are converted to non-editable images. When the document is converted, these images are refreshed to 2007 Office release again. When a user selects SmartArt in Word 2007, the Diagram Gallery from Word 2003 appears. \\
Vertical Text Box Alignment & Vertical text box alignment of center or bottom are new to Word 2007. & Vertical text box alignment of center or bottom is permanently converted to top vertical text box alignment. \\
Math & Equation building is new to Word 2007. & Equations are represented as non-editable images. These images are refreshed when the document is converted. The Equations UI is disabled in compatibility mode.
\end{longtable}
\end{center}
